---
title: "LLMB R package"
description: "Real-time Search Based on a Keyword "
date: last-modified
bibliography: references.bib
author:
  - name: Xinzhuo Huang
    orcid: 0009-0007-6448-5114
    email: xhuangcb@connect.ust.hk
    affiliations:
     - name: HKUST SOSC
title-block-banner: "#8F999F"
citation: 
    author: Huang Xinzhuo
format: 
  html:
    code-line-numbers: true
    code-block-bg: true
    code-block-border-left: "#ffffff"
    code-tools:
      caption: "Source Code"
    smooth-scroll: true
    linestretch: 1.2
    df-print: paged
    theme:
      light: [flatly]
      dark: [darkly]
    code-fold: true
    code-summary: "Show the R code"
    toc: false
    citation-location: margin  
    reference-location: margin
    citations-hover: true
    toc-location: right
    number-sections: true
    monofont: Georia
    mainfont: Cambria Math
    link-citations: yes
    comments:
      giscus:
        repo: xinzhuohkust/comments
      hypothesis:
        theme: clean

execute:
    warning: false
    message: false
    error: false
---
```{=html}
<style>
body {text-align: justify}
</style>
```
A package that allows political scientists to perform real-time searches on government responsiveness data within the [Local Leader Message Board](https://liuyan.people.com.cn/), a national platform for petitioning in China @su2016selective. Utilizing the `V8` package, this tool provides a JavaScript environment for [crypto-js](https://www.npmjs.com/package/crypto-js) within R, proving to be extremely helpful for reverse engineering during web scraping tasks. While currently a simple package, further development is underway to add advanced features such as additional data sources and visualization capabilities.

# Installation 

```{r}
#| eval: false
#| code-fold: false
remotes::install_github("xinzhuohkust/LLMB")

library(LLMB)
```

# Usage 

## Single keywords
```{r}
#| eval: false
#| code-fold: false
keyword_search(
  keywords = "恒大",
  page = 1,
  rows = 10, # or 500
  format = "tibble" # JSON or string
)
```

## Multi keywords

```{r}
#| eval: false
#| code-fold: false
tibble(
    keywords = c("恒大", "碧桂园", "跑路")
) %>%
    group_by(keywords) %>%
    reframe(page = list(1:10)) %>%
    unnest(page) %>%
    mutate(
        data = map2(
            keywords,
            page,
            ~ keyword_search(.x, .y, rows = 500),
            .progress = TRUE
        )
    )
```
```{r}
#| echo: false
pacman::p_load(tidyverse, DT) 

read_rds("sample_data/sample_data.Rds")
```

# Call `crypto-js` into R

```{r}
#| code-fold: false
cryptojs_env <- get(".cryptojs_env", envir = asNamespace("LLMB"))
```